\normalfont\spacedallcaps{}

### 2019-02-20 Document/article_4.tex
bar-plots

Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:4}. figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome. we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs. The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos}{here}. you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput/Logos/BubblePlots}{here}. we have 11 pages and each page has 21 models for all tRNA classes in a cluster. 
\begin{table}[hbt] 
\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
        \parbox{.45\textwidth} {\begin{enumerate}
            \item LspMARLEM2494
            \item LenriettiiLEM3045
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TbruceigambienseDAL972
            \item TbruceiLister427
            \item TbruceiTREU927
            \item TevansiSTIB805
            \item TcongolenseIL3000
            \item TvivaxY486
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TgrayiANR4
            \item TrangeliSC58
            \item TcruziCLBrener
            \item TcruziCLBrenerEsmeraldo-like
            \item TcruziCLBrenerNon-Esmeraldo-like
            \item TcruzicruziDm28c
            \item TcruziDm28c
            \item TcruziEsmeraldo
            \item TcruziJRcl4
            \item TcruzimarinkelleiB7
            \item TcruziSylvioX10-1
            \item TcruziSylvioX10-1-2012
            \item TcruziTulacl2
            \item TtheileriEdinburgh
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item CfasciculataCfCl
            \item LseymouriATCC30220
            \item LpyrrhocorisH10
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LmajorFriedlin
            \item LmajorLV39c5
            \item LmajorSD75
            \item LturanicaLEM423
            \item LarabicaLEM1108
            \item LtropicaL590
            \item LaethiopicaL147
            \item LgerbilliLEM452
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LdonovaniBHU1220
            \item LdonovaniBPK282A1
            \item LinfantumJPCM5
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lamazonensis\\
                  MHOMBR71973M2269
            \item Lmexicana\\MHOMGT2001U1103
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lbraziliensis\\MHOMBR75M2904
            \item Lbraziliensis\\MHOMBR75M2903
            \item Lpanamensis\\MHOMPA94PSC1
            \item Lpanamensis\\MHOMCOL81L13
        \end{enumerate}}\\
        \bottomrule
\end{tabular}
\label{table:4}
\end{adjustbox}
\end{table}

>>>>

Using phylogenetic trees of Trypanosoma from these works \cite{Souza:2018dg,Hughes:2003,Pothirat:2014,Kelly:2017}, we grouped TryTryp genomes as table \ref{table:4}. figure \ref{fig:countsclustered} shows a summery of the number of tRNA genes for each cluster and figure \ref{fig:funcclustered} shows the tRNA functional classes not annotated for clusters of genome. we excluded genome PconfusumCUL13 from the study, until we find a well sequenced version of this genome for which we can annotate all 22 functional classes of tRNAs. The Logo data for TryTryp genomes and Human can be found \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/Logos}{here}. you can find the bubble plots for each cluster \href{https://github.com/fhadinezhadUC/Leishmania_2019/tree/master/Results/tsfmInput-output/output/BubblePlots}{here}. we have 11 pages and each page has 21 models for all tRNA classes in a cluster. 
\begin{table}[hbt] 
\caption{Classification of TryTryp genomes. genomes not mentioned here are clustered as one genome.}
\begin{adjustbox}{width=\columnwidth,center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
        \toprule LenriettiComplex & AfricanTrypanosome & AmericanTrypanosome & Leishmania1 & Leishmania2 &LDonovaniComplex & LMexicanaComplex & Lvianna \\\midrule
        \parbox{.45\textwidth} {\begin{enumerate}
            \item LspMARLEM2494
            \item LenriettiiLEM3045
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TbruceigambienseDAL972
            \item TbruceiLister427
            \item TbruceiTREU927
            \item TevansiSTIB805
            \item TcongolenseIL3000
            \item TvivaxY486
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item TgrayiANR4
            \item TrangeliSC58
            \item TcruziCLBrener
            \item TcruziCLBrenerEsmeraldo-like
            \item TcruziCLBrenerNon-Esmeraldo-like
            \item TcruzicruziDm28c
            \item TcruziDm28c
            \item TcruziEsmeraldo
            \item TcruziJRcl4
            \item TcruzimarinkelleiB7
            \item TcruziSylvioX10-1
            \item TcruziSylvioX10-1-2012
            \item TcruziTulacl2
            \item TtheileriEdinburgh
        \end{enumerate}} & \parbox{.45\textwidth}{\begin{enumerate}
            \item CfasciculataCfCl
            \item LseymouriATCC30220
            \item LpyrrhocorisH10
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LmajorFriedlin
            \item LmajorLV39c5
            \item LmajorSD75
            \item LturanicaLEM423
            \item LarabicaLEM1108
            \item LtropicaL590
            \item LaethiopicaL147
            \item LgerbilliLEM452
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item LdonovaniBHU1220
            \item LdonovaniBPK282A1
            \item LinfantumJPCM5
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lamazonensis\\
                  MHOMBR71973M2269
            \item Lmexicana\\MHOMGT2001U1103
        \end{enumerate}}& \parbox{.45\textwidth}{\begin{enumerate}
            \item Lbraziliensis\\MHOMBR75M2904
            \item Lbraziliensis\\MHOMBR75M2903
            \item Lpanamensis\\MHOMPA94PSC1
            \item Lpanamensis\\MHOMCOL81L13
        \end{enumerate}}\\
        \bottomrule
\end{tabular}
\label{table:4}
\end{adjustbox}
\end{table}
